### 2023-12-17 documentation/thesis/thesis_document.tex
more thesis

At the current state of implementation, it is only possible to detect
and use sensors that are directly connected to the \gls{pc} with the
library. This has the disadvantage that there must always be a physical
connection. This can make it difficult to install multiple sensors in
measurement setups where space or cable routing options are limited. To
make sensors connected to a small \passthrough{\lstinline!remote!}
\gls{pc} available on the network, the
\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
been developed. This can be a single board computer (e.g.~a Raspberry
Pi). The small footprint and low power consumption make it a good
choice. It can also be used in a temperature chamber. The approach of
implementing this via a \gls{rest} interface also offers the advantage
that several measurements or experiments can be recorded at the same
time with the sensors.

@@

@@

In the first version of this library, the user had to write his own
Python scripts even for short measurement and visualisation tasks.
However, this was already time-consuming for reading out a sensor and
configuring the measurement parameters and metadata and quickly required
more than 100 lines of new Python code. Although such examples are
provided in the documentation, it must be possible for programming
beginners in particular to use them. To simplify these tasks, a
\gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
around this library, which is then also supplied as a fixed component.
This \gls{cli} implements the following functionalities:

@@

Thanks to this functionality of the \gls{cli}, it is now possible to
connect a sensor to the \gls{pc}, configure a measurement series with it
and run it at the end. The result is then an exported file with the
measured values. These can then be read in again with the library and
processed further. The following\ref{lst:mrpcli_config_run} bash code
shows this procedure in detail:

@@

\ref{example_measurement_analysis_pipeline.png}

\begin{itemize}
\tightlist
\item
  datenanalyse für nicht programmieruer
\item
  automatisierter aufbau der call-tree
\item
  mit typcheck
\item
  alle funktionen mit bestimmer signtur werden automatisch aus globals
  geladen und stehen nutzer zur verfühung
\end{itemize}

\begin{lstlisting}[caption={Example User Defined Processing Pipeline}]
stage import_readings:
  function: import_readings
  parameters:
    IP_input_folder: ./readings/fullsphere/
    IP_file_regex: 360_(.)*.mag.json

@@

@@

Software tests in libraries offer numerous advantages for improving
quality and efficiency. Firstly, they enable the identification of
errors and vulnerabilities before software is published as a new
version. This significantly improves the reliability of library
applications. Tests also ensures consistent and reliable performance,
which is particularly important when libraries are used by different
users and for different usecases.

@@

During the development of the library, test cases were also created for
all important functionalities and use cases. The test framework
\passthrough{\lstinline!PyTest!}\cite{PyTest} was used for this
purpose, as it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. It
also allows to tag tests, which is useful for grouping tests or
excluding certain tests in certain build environment scenarios. Since
all intended use cases were mapped using the test cases created, the
code of the test cases could later be used in slightly simplified
variants\ref{lst:pytest_example_code} as examples for the documentation.

@@

One problem, however, is the parts of the library that require direct
access to external hardware. These are, for example, the
\passthrough{\lstinline!MRPHal!} and
\passthrough{\lstinline!MRPHalRest!} modules, which are required to read
out sensors connected via the network. Two different approaches were
used here. In the case of local development, the test runs were carried
out on a \gls{pc} that can reach the network hardware and thus the test
run could be carried out with real data.

@@

One important point that improves usability for users is the simple
installation of the library. As it was created in the Python programming
language, there are several public package directories where users can
provide their software modules. Here,
\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
is the most commonly used package directory and offers direct support
for the package installation programm
\gls{pip}\ref{lst:setup_lib_with_pip}.

@@

\begin{lstlisting}[language=bash, caption={Bash commands to install the MagneticReadoutProcessing library using pip}, label=lst:setup_lib_with_pip]
# https://pypi.org/project/MagneticReadoutProcessing/
# install the latest version
$ pip3 install MagneticReadoutProcessing
# install the specific version 1.4.0
$ pip3 install MagneticReadoutProcessing==1.4.0
\end{lstlisting}

To make the library compatible with the package directory, Python
provides separate installation routines that build a package in an
isolated environment and then provide an installation
\passthrough{\lstinline!wheel!} archive. This can then be uploaded to
the package directory.

Since the library requires additional dependencies
(e.g.~\passthrough{\lstinline!numpy!},
\passthrough{\lstinline!matplotlib!}), which cannot be assumed to be
already installed on the target system, these must be installed prior to
the actual installation. These can be specified in the library
installation configuration
\passthrough{\lstinline!setup.py!}\ref{lst:setup_py_req} for this
purpose.

@@

In addition, these commands are available globally in the system without
the terminal shell being located in the library folder.

@@

In order to make the documentation created by
\passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
with the package management by \passthrough{\lstinline!PyPi!} services,
which provide Python library documentation online.

>>>>

At the current state of implementation, it is only possible to detect
and use sensors that are directly connected to the \gls{pc} with the
\gls{mrp}-library. This has the disadvantage that there must always be a
physical connection. This can make it difficult to install multiple
sensors in measurement setups where space or cable routing options are
limited. To make sensors connected to a small
\passthrough{\lstinline!remote!} \gls{pc} available on the network, the
\passthrough{\lstinline!Proxy!}\ref{MRPlib_Proxy_Module.png} module has
been developed. This can be a single board computer (e.g.~a Raspberry
Pi). The small footprint and low power consumption make it a good
choice. It can also be used in a temperature chamber. The approach of
implementing this via a \gls{rest} interface also offers the advantage
that several measurements or experiments can be recorded at the same
time with the sensors.

@@

Usability improvements in software libraries are crucial for efficient
and user-friendly development. Intuitive API documentation, clearly
structured code examples and improved error messages promote a smooth
developer experience. Standardised naming conventions and well
thought-out default values simplify the application. A \gls{gui} or
\gls{cli} application for complex libraries can make it easier to use,
especially for developers with less experience. Continuous feedback
through automated tests and comprehensive error logs enable faster bug
fixing. The integration of community feedback and regular updates
promotes the adaptability of the \gls{mrp}-library to changing needs.
Effective usability improvements help to speed up development processes
and increase the satisfaction of the developer community. In the
following, some of these have been added in and around the
\gls{mrp}-library, but they are only optional components for the
intended use.

@@

In the first version of this \gls{mrp}-library, the user had to write
his own Python scripts even for short measurement and visualisation
tasks. However, this was already time-consuming for reading out a sensor
and configuring the measurement parameters and metadata and quickly
required more than 100 lines of new Python code. Although such examples
are provided in the documentation, it must be possible for programming
beginners in particular to use them. To simplify these tasks, a
\gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
around this \gls{mrp}-library, which is then also supplied as a fixed
component. This \gls{cli} implements the following functionalities:

@@

Thanks to this functionality of the \gls{cli}, it is now possible to
connect a sensor to the \gls{pc}, configure a measurement series with it
and run it at the end. The result is then an exported file with the
measured values. These can then be read in again with the
\gls{mrp}-library and processed further. The bash
code\ref{lst:mrpcli_config_run} shows this procedure in detail.

@@

After it is very easy for users to carry out measurements using the
\gls{cli}, the next logical step is to analyse the recorded data. This
can involve one or several hundred data records. Again, the procedure
for the user is to write their own evaluation scripts using the
\gls{mrp}-library. This is particularly useful for complex analyses or
custom algorithms, but not necessarily for simple standard tasks such as
bias compensation or graphical plot outputs. For this purpose, a further
\gls{cli} application was created, which enables the user to create and
execute complex evaluation pipelines for measurement data without
programming. The example\ref{example_measurement_analysis_pipeline.png}
shows a typical measurement data analysis pipeline, which consists of
the following steps:

\begin{itemize}
\tightlist
\item
  Import the measurements
\item
  Determine sensor bias value from imported measurements using a
  reference measurement
\item
  Apply linear temperature compensation
\item
  Export the modified measurements
\item
  Create a graphical plot of all measurements with standard deviation
\end{itemize}

In order to implement such a pipeline, the
\passthrough{\lstinline!yaml!} file format was chosen for the definition
of the pipeline, as this is easy to understand and can also be easily
edited with a text editor. Detailed examples can be found in the
documentation\cite{MagneticReadoutProcessingReadTheDocs}. The
pipeline definition consists of sections which execute the appropriate
Python commands in the background. The signatures in the
\passthrough{\lstinline!yaml!} file are called using
\passthrough{\lstinline!reflection!} and a real-time search of the
loaded
\passthrough{\lstinline!global() symbol table!}\cite{PythonGlobalSymbolTable}.
This system makes almost all Python functions available to the user. To
simplify use, a pre-defined list of tested \gls{mrp} library functions
for use in pipelines is listed in the
documentation\cite{MagneticReadoutProcessingReadTheDocs}. The
following pipeline definition\ref{lst:mrpuddp_example_yaml} shows the
previously defined steps\ref{example_measurement_analysis_pipeline.png}
as \passthrough{\lstinline!yaml!} syntax.

\begin{lstlisting}[caption={Example User Defined Processing Pipeline}, label=lst:mrpuddp_example_yaml]
stage import_readings:
  function: import_readings
  parameters:
    IP_input_folder: ./readings/fullsphere/
    IP_file_regex: 360_(.)*.mag.json

@@

\begin{itemize}
\tightlist
\item
  blöcke erleutern insbesondere stage
\item
  wie calltree gebildet
\end{itemize}

@@

Software tests in libraries offer numerous advantages for improving
quality and efficiency. Firstly, they enable the identification of
errors and vulnerabilities before software is published as a new
version. This significantly improves the reliability of
\gls{mrp}-library applications. Tests also ensures consistent and
reliable performance, which is particularly important when libraries are
used by different users and for different usecases.

@@

During the development of the \gls{mrp}-library, test cases were also
created for all important functionalities and use cases. The test
framework \passthrough{\lstinline!PyTest!}\cite{PyTest} was used for
this purpose, as it offers direct integration in most \gls{ide}s (see
\ref{MRP_library_test_results_for_different_submodules_executed_in_PyCharm_(+ide).png})
and also because it provides detailed and easy-to-understand test
reports as output in order to quickly identify and correct errors. It
also allows to tag tests, which is useful for grouping tests or
excluding certain tests in certain build environment scenarios. Since
all intended use cases were mapped using the test cases created, the
code of the test cases could later be used in slightly simplified
variants\ref{lst:pytest_example_code} as examples for the documentation.

@@

One problem, however, is the parts of the \gls{mrp}-library that require
direct access to external hardware. These are, for example, the
\passthrough{\lstinline!MRPHal!} and
\passthrough{\lstinline!MRPHalRest!} modules, which are required to read
out sensors connected via the network. Two different approaches were
used here. In the case of local development, the test runs were carried
out on a \gls{pc} that can reach the network hardware and thus the test
run could be carried out with real data.

@@

One important point that improves usability for users is the simple
installation of the \gls{mrp}-library. As it was created in the Python
programming language, there are several public package directories where
users can provide their software modules. Here,
\passthrough{\lstinline!PyPi!}\cite{PyPI}\ref{MagneticReadoutProcessing_library_hosted_on_PyPi.png}\cite{MagneticReadoutProcessingPyPI}
is the most commonly used package directory and offers direct support
for the package installation programm
\gls{pip}\ref{lst:setup_lib_with_pip}.

@@

\begin{lstlisting}[language=bash, caption={Bash commands to install the MagneticReadoutProcessing (+mrp)-library using pip}, label=lst:setup_lib_with_pip]
# https://pypi.org/project/MagneticReadoutProcessing/
# install the latest version
$ pip3 install MagneticReadoutProcessing
# install the specific version 1.4.0
$ pip3 install MagneticReadoutProcessing==1.4.0
\end{lstlisting}

To make the \gls{mrp}-library compatible with the package directory,
Python provides separate installation routines that build a package in
an isolated environment and then provide an installation
\passthrough{\lstinline!wheel!} archive. This can then be uploaded to
the package directory.

Since the \gls{mrp}-library requires additional dependencies
(e.g.~\passthrough{\lstinline!numpy!},
\passthrough{\lstinline!matplotlib!}), which cannot be assumed to be
already installed on the target system, these must be installed prior to
the actual installation. These can be specified in the \gls{mrp}-library
installation configuration
\passthrough{\lstinline!setup.py!}\ref{lst:setup_py_req} for this
purpose.

@@

In addition, these commands are available globally in the system without
the terminal shell being located in the \gls{mrp}-library folder.

@@

In order to make the documentation created by
\passthrough{\lstinline!Sphinx!} accessible to the user, there are, as
with the package management by \passthrough{\lstinline!PyPi!} services,
which provide Python \gls{mrp}-library documentation online.
